Replication Survey

### 2023-08-17 docs/manuscript/manuscript.tex
Updates from Overleaf

\author{
\name{Peter Kedron\textsuperscript{a,b}\thanks{CONTACT Peter Kedron. Email: Peter.Kedron@asu.edu}, Joseph Holler\textsuperscript{c}, and Sarah Bardin\textsuperscript{a,b}}
\affil{\textsuperscript{a}School of Geographical Sciences and Urban Planning, Arizona State University, Tempe, Arizona, USA; \textsuperscript{b}Spatial Analysis Research Center (SPARC), Arizona State University, Tempe, Arizona, USA; \textsuperscript{c}Department of Geography, Middlebury College, Middlebury, Vermont, USA}
}

@@

>>>>

\author{
\name{Peter Kedron\textsuperscript{a,b}\thanks{CONTACT Peter Kedron. Email: peterkedron@ucsb.edu}, Joseph Holler\textsuperscript{d}, and Sarah Bardin\textsuperscript{a,c}}
\affil{\textsuperscript{a} Department of Geography, University of California Santa Barbara, Santa Barbara, California, USA; \textsuperscript{b}School of Geographical Sciences and Urban Planning, Arizona State University, Tempe, Arizona, USA; \textsuperscript{c}Spatial Analysis Research Center (SPARC), Arizona State University, Tempe, Arizona, USA; \textsuperscript{d}Department of Geography, Middlebury College, Middlebury, Vermont, USA}
}

@@

To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of replicability, beliefs about what factors affects the chances or replicating a study, motivations to attempt replication studies, and experiences conducting replications.
To support generalization, we designed a sampling frame to capture researchers from across disciplinary subfields and methodological approaches, and draw survey participants from that frame using a probability sampling scheme.
In the remainder of this paper, we first present the design of our survey, sampling strategy, and analytical approach. 
We then present the results of our survey before discussing the implications and limitations of our work.
